Bringing the Power of eBPF to Open vSwitch

### 2018-10-25 paper.tex
abstract: Minor grammar fixes

\begin{abstract}
eBPF is an emerging technology in Linux kernel with the goal of making Linux kernel
extensible by providing an eBPF virtual machine with safety guarantee.
Open vSwitch, OVS, is a software switch running majorly in Linux
operating systems, its fast path packet process is implemented in Linux kernel
module, openvswitch.ko.
To provide greater flexibility and extensibility to OVS datapath, in this
work, we present our design on making use of eBPF technology in OVS datapath
development with two projects: the OVS-eBPF project and the OVS-AFXDP project.
The goal of OVS-eBPF project is to re-write existing flow processing features
in openvswitch kernel datapath into eBPF program, and attaching it
to Linux TC.
On the other hand, the OVS-AFXDP project aims to by-passing the kernel
using AF\_XDP socket and moves most of the flow processing features
into userspace.
We demonstrate the feasibility of implementing OVS datapath with the
aforementioned technologies and present the performance number in this paper.
\end{abstract}

>>>>

\begin{abstract}
eBPF is an emerging technology in Linux kernel with the goal of making Linux kernel
extensible by providing an eBPF virtual machine with safety guarantee.
Open vSwitch (OVS), is a software switch running majorly in Linux
operating systems, its fast path packet process is implemented in Linux kernel
module, openvswitch.ko.
To provide greater flexibility and extensibility to OVS datapath, in this
work, we present our design on making use of eBPF technology in OVS datapath
development with two projects: the OVS-eBPF project and the OVS-AFXDP project.
The goal of OVS-eBPF project is to re-write existing flow processing features
in openvswitch kernel datapath into eBPF program, and attaching it
to Linux TC.
On the other hand, the OVS-AFXDP project aims to by-pass the kernel
using an AF\_XDP socket and moves most of the flow processing features
into userspace.
We demonstrate the feasibility of implementing OVS datapath with the
aforementioned technologies and present the performance numbers in this paper.
\end{abstract}
